Supplementary Material

### 2022-01-18 supplement/supplement.Rmd
CD revision 1, updaating manuscript and supplement

---
title: "Supplementary Material"
subtitle: "*Can real-world stimuli improve cognitive performance for children living in adversity?*"
output:
   bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: false
    lof: yes
    toc: false
    extra_dependencies: ["booktabs","caption","longtable","float"]
    keep_tex: true
geometry: margin=.5in
mainfont: Times
fontsize: 11pt
urlcolor: blue
header-includes:
- \usepackage{siunitx}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.align = 'center', fig.pos = "H", fig.show = 'asis')

library(tidyverse)
library(gt)

load("staged-objects.Rdata")
```

@@

This document contains two parts. First, we report our full multiverse primary analyses, including covariates (e.g., age and distractions during cognitive testing). Second, we provide visualizations for both of our secondary, exploratory analyses. The first set were focused on exploring the components of adversity dimensions. The second focuses on comparing violence $\times$ task version interaction with poverty $\times$ task version interaction.

@@

@@

### SI Table 1. Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for all terms predicting attention shifting. {#tab1}

```{r sitables1, results='asis'}
si_table.01.1 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  cat()
```

@@

### SI Figure 1. Unpredictability and Attention Shifting specification plot with all covariates. {#fig1}

```{r sifig1, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_unp
```

@@

### SI Figure 2. Violence exposure and Attention Shifting specification plot with all covariates. {#fig2}

```{r sifig2, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_vio
```

@@

### SI Figure 3. Poverty and Attention Shifting specification plot with all covariates. {#fig3}

```{r sifig3, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_ses
```

@@

### SI Figure 4. Unpredictability and working memory updating specification plot with all covariates. {#fig4}

```{r sifig4, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_unp
```

@@

### SI Figure 5. Violence exposure and working memory updating specification plot with all covariates. {#fig5}

```{r sifig5, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_vio
```

@@

### SI Figure 6. Poverty and working memory updating specification plot with all covariates. {#fig6}

```{r sifig6, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_ses
```

@@

### SI Table 2. Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for main effects of adversity components and interactions with task version for attention shifting and working memory updating.{#tab2}

```{r sitables2, results='asis'}
si_table.02.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
  cat()
```

@@

### SI Table 3. Median simple slopes (unstandardized) and percent significant for adversity component interactions with task version for attention shifting and working memory updating. {#tab3}

```{r sitables3, results='asis'}
si_table.03.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  cat()
```

@@

### SI Figure 7. Unpredictability components and attention shifting multiverse results. {#fig7}

```{r sifig7, fig.width=8, fig.height=7.5, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
unp_shifting
```

@@

### SI Figure 8. Violence exposure components and attention shifting multiverse results. {#fig8}

```{r sifig8, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
vio_shifting
```

@@

### SI Figure 9. Poverty components and attention shifting multiverse results. {#fig9}

```{r sifig9, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
ses_shifting
```

@@

### SI Figure 10. Unpredictability components and working memory updating multiverse results. {#fig10}

```{r sifig10, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions"}
unp_updating
```

@@

### SI Figure 11. Violence exposure components and working memory updating multiverse results. {#fig11}

```{r sifig11, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
vio_updating
```

@@

### SI Figure 12. Poverty components and working memory updating multiverse results. {#fig12}

```{r sifig12, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
ses_updating
```

@@

### SI Table 4. Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for multiverse analyses comparing Poverty $\times$ task version and violence $\times$ task version interactions.{#tab4}

```{r sitables4, results='asis'}
si_table.04.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
  cat()
```

### SI Table 5. Median simple slopes (unstandardized) and percent significant for multiverse analyses comparing Poverty $\times$ task version and violence $\times$ task version interactions. {#tab5}

```{r sitables5, results='asis'}
si_table.05.0 %>%
  as_latex() %>%
  as.character() %>%
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>%
  cat()
```

@@

### SI Figure 13. Multiverse results for Poverty and violence exposure interactions with task version in the same model. {#fig13}

@@

>>>>

---
title: "Supplementary Material"
subtitle: "*Hidden Talents in Context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth*"
output:
  officedown::rdocx_document:
    reference_docx: reference-doc.docx
    page_size:
      width: 8.5
      height: 11
      orient: "portrait"
    page_margins:
      bottom: .5
      top: .5
      right: .25
      left: .25
      header: 0
      footer: 0
      gutter: 0
    plots:
      align: center
      style: Normal
      caption:
        style: Image Caption
        pre: 'SI Figure '
        sep: '. '
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Caption
        pre: 'SI Table '
        sep: '. '
---

```{r setup, include=FALSE}
# load libraries
library(tidyverse)
library(officer)
library(officedown)
library(flextable)

# set up chunk options
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!t", 
  fig.show = "asis",
  fig.width = 8, 
  fig.height = 7.5,
  dpi = 600,
  out.extra = "",
  message = F,
  tab.topcaption = T,
  warning = F
)

# set up flextable for tables
set_flextable_defaults(
  font.family = "Times", 
  font.size = 10,
  font.color = "black",
  line_spacing = 1,
  padding.bottom = 1, 
  padding.top = 1,
  padding.left = 1,
  padding.right = 1
)

# load all data and objects
load("staged-objects.Rdata")
```

@@

This document contains three parts. First, we report our full multiverse primary analyses, including covariates (e.g., age and distractions during cognitive testing). Second, we provide visualizations for both of our secondary, exploratory analyses. The first set were focused on exploring the components of adversity dimensions. The second focuses on comparing violence $\times$ task version interaction with poverty $\times$ task version interaction. Third, we report descriptive statistics and bivariate correlations among all indices of adversity (unpredictability, violence, and poverty exposure).

@@

**[Descriptive Statistics for all Adversity Indices](#sec3)**

- [SI Table 6](#tab6) (Unpredictability)
- [SI Table 7](#tab7) (Violence Exposure)
- [SI Table 8](#tab8) (Poverty)

@@

### Median Effect Sizes {#tab1}

```{r sitables1, tab.id = "sitables1", tab.cap = "Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for all terms predicting attention shifting."}
si_table.01.1$`_data` %>% 
  add_column(.after = 6,"empty1" = "") %>% 
  add_row(.before = 1, "mod_term_label" = "Unpredictability") %>% 
  add_row(.after = 6, "mod_term_label" = "Violence") %>% 
  add_row(.after = 12, "mod_term_label" = "Poverty") %>%
  select(-iv) %>% 
  flextable() %>% 
  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 7, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 12, j1 = 1, j2 = 10) %>% 
  bold(i = c(1,7,13), j = 1) %>% 
  padding(i = c(2:6, 8:12, 14:18), j = 1, padding.left = 10) %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(
    iv = "", mod_term_label = "Term", 
    empty1 = "", 
    ci_shifting = "95% CI", 
    ci_updating = "95% CI"
    ) %>% 
  add_header_row(
    values = c(" ", "Attention Shifting", " ", "Working Memory Updating"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2,7), as_paragraph(as_i("N")), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph("\U1D6FD"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 18, border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  set_table_properties(width = 1, layout = "autofit")
```

@@

### Unpredictability and Attention Shifting specification plot with all covariates. {#fig1}

```{r sifig1, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
shifting_unp
```

@@

### Violence exposure and Attention Shifting specification plot with all covariates. {#fig2}

```{r sifig2, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
shifting_vio
```

@@

### Poverty and Attention Shifting specification plot with all covariates. {#fig3}

```{r sifig3, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
shifting_ses
```

@@

### Unpredictability and working memory updating specification plot with all covariates. {#fig4}

```{r sifig4, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
updating_unp
```

@@

### Violence exposure and working memory updating specification plot with all covariates. {#fig5}

```{r sifig5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
updating_vio
```

@@

### Poverty and working memory updating specification plot with all covariates. {#fig6}

```{r sifig6, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
updating_ses
```

@@

### Median Effect Sizes {#tab2}

```{r sitables2, tab.id = "sitables2", tab.cap = "Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for main effects of adversity components and interactions with task version for attention shifting and working memory updating."}
si_table.02.0$`_data` %>% 
  mutate(mod_term_label = str_replace(mod_term_label,"\\$\\\\times\\$","x")) %>% 
  add_column(.after = 6,"empty1" = "") %>% 
  add_row(.before = 1, "mod_term_label" = "Unpredictability") %>% 
  add_row(.after = 7, "mod_term_label" = "Violence") %>% 
  add_row(.after = 14, "mod_term_label" = "Poverty") %>%
  select(-iv) %>% 
  flextable() %>% 
  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 8, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 15, j1 = 1, j2 = 10) %>% 
  bold(i = c(1,8,15), j = 1) %>% 
  padding(i = c(2:7, 9:14, 16:23), j = 1, padding.left = 10) %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(
    iv = "", mod_term_label = " ", 
    empty1 = "", 
    ci_shifting = "95% CI", 
    ci_updating = "95% CI"
  ) %>% 
  add_header_row(
    values = c(" ", "Attention Shifting", " ", "Working Memory Updating"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2,7), as_paragraph(as_i("N")), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph("\U1D6FD"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  align(i = 2, j = 1, align = "left", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 23, border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  set_table_properties(width = 1, layout = "autofit")
```

@@

### Median Simple Effects {#tab3}

```{r sitables3, tab.id = "sitables3", tab.cap = " Median simple slopes (unstandardized) and percent significant for adversity component interactions with task version for attention shifting and working memory updating."}
si_table.03.0$`_data` %>% 
  add_column(.after = 6,"empty1" = "") %>% 
  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
  add_row(.after = 11, "iv" = "Working Memory Updating") %>%
  select(-dv) %>% 
  flextable() %>% 
  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 12, j1 = 1, j2 = 10) %>% 
  bold(i = c(1,12), j = 1) %>% 
  padding(i = c(2:11, 13:22), j = 1, padding.left = 10) %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(iv = "", empty1 = "") %>% 
  add_header_row(
    values = c(" ", "Task Version", " ", "Adversity Exposure"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = c(11,22), border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  fontsize(size = 11, part = "body") %>% 
  set_table_properties(width = 1, layout = "autofit")
```

@@

### Unpredictability components and attention shifting multiverse results. {#fig7}

```{r sifig7, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
unp_shifting
```

@@

### Violence exposure components and attention shifting multiverse results. {#fig8}

```{r sifig8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
vio_shifting
```

@@

### Poverty components and attention shifting multiverse results. {#fig9}

```{r sifig9, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
ses_shifting
```

@@

### Unpredictability components and working memory updating multiverse results. {#fig10}

```{r sifig10, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
unp_updating
```

@@

### Violence exposure components and working memory updating multiverse results. {#fig11}

```{r sifig11, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
vio_updating
```

@@

### Poverty components and working memory updating multiverse results. {#fig12}

```{r sifig12, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
ses_updating
```

@@

### Median Effects {#tab4}

```{r sitables4, tab.id = "sitables4", tab.cap = "Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for multiverse analyses comparing Poverty by task version and violence by task version interactions."}
si_table.04.0$`_data` %>% 
  mutate(mod_term_label = str_replace(mod_term_label,"\\$\\\\times\\$","x")) %>% 
  flextable() %>% 
  set_header_labels(
    iv = "", mod_term_label = " ", 
    empty1 = "", 
    ci = "95% CI"
  ) %>% 
  compose(i = 1, j = c(2), as_paragraph("\U1D6FD"), part = "header") %>% 
  compose(i = 1, j = c(4), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  compose(i = 1, j = c(5), as_paragraph("median ", as_i("N")), part = "header") %>% 
  add_footer_row(
    values = " ",
    colwidths = 5
  ) %>% 
  set_table_properties(width = 1, layout = "autofit")
```

### Median Simple Effects {#tab5}

```{r sitables5, tab.id = "sitables5", tab.cap = "Median simple slopes (unstandardized) and percent significant for multiverse analyses comparing Poverty by task version and violence by task version interactions."}
si_table.05.0$`_data` %>% 
  add_column(.after = 5,"empty1" = "") %>% 
  flextable() %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(iv = "", empty1 = "") %>% 
  add_header_row(
    values = c(" ", "Task Version", " ", "Adversity Exposure"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = c(2), border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  fontsize(size = 11, part = "body") %>%
  add_footer_row(
    values = " ",
    colwidths = 10
  ) %>% 
  set_table_properties(width = 1, layout = "autofit")
```

@@

### Multiverse results for Poverty and violence exposure interactions with task version in the same model. {#fig13}

@@

# Descriptive Statistics of Adversity Indices {#sec3}

```{r sitables6, tab.id = "sitables6", tab.cap = "Correlations and descriptive statistics for interview-based and perceived unpredictability."}
si_table.06.0 %>% 
  flextable() %>% 
  set_header_labels(Variable = "") %>% 
  set_table_properties(width = 1, layout = "autofit") %>% 
  add_footer_row(
    values = " ",
    colwidths = 5
  ) %>% 
  add_footer_row(
    values = " ",
    colwidths = 5
  ) %>% 
  compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
    part = "footer"
  ) 
```

```{r sitables7, tab.id="sitables7", tab.cap="Correlations and descriptive statistics for witnessing and involvement in fights and perceived neighborhood violence. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
si_table.07.0 %>% 
  flextable() %>% 
  set_header_labels(Variable = "") %>% 
  set_table_properties(width = 1, layout = "autofit") %>% 
  add_footer_row(
    values = " ",
    colwidths = 4
  ) %>% 
  add_footer_row(
    values = " ",
    colwidths = 4
  ) %>% 
  compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
    part = "footer"
  ) 
```

```{r sitables8, tab.id="sitables8", tab.cap="Correlations and descriptive statistics for interview, school, and perceived poverty variables."}
si_table.08.0 %>% 
  flextable() %>% 
  set_header_labels(Variable = "") %>% 
  set_table_properties(width = 1, layout = "autofit") %>% 
  add_footer_row(
    values = " ",
    colwidths = 5
  ) %>% 
  add_footer_row(
    values = " ",
    colwidths = 5
  ) %>% 
  compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
    part = "footer"
  ) 
```
